---
title: "Examine Data"
author: "Ernesto Guardia"
date: "January 23, 2017"
output: html_document
---

```{r, echo=FALSE}

hbat <- read.csv("HBAT.csv")

```

We are currently working with the HBAT dataset which has `r ncol(hbat)` variables for `r nrow(hbat)` observations. This is a made-up dataset consisting of both metric and non-metric variables.

The sections to be covered in this document are the following:

1. [Normality Test]
2. [Relation Test]
3. [Correlation Table]
4. [Outlier Test]
5. [Scatterplot Matrix]

# Normality Test {#t1_normality}

The following normality test is used to test the normality assumption for the metric variables (x6 through x22), as non-metric variables won't be normal. The process to test normality will be done in three steps:

* Visual examination of histogram
* Shapiro-Wilk test
* Visual confirmation of normality assumption through QQPlots

Below, you can see an example on how to perform it on variable x6.

```{r, fig.align='center'}

# Plot densities
plot(density(hbat$x6), main='Histogram for x6')

#Shapiro-Wilk test
shapiro.test(hbat$x6)

#H0: Data comes from a normal distribution
#Ha: Data does not come from a normal distribution

#Based on an alpha value of 0.05, we can reject the null hypothesis and conclude that the data does not come from a normal distribution.

#QQPlot
qqnorm(hbat$x6)
qqline(hbat$x6, col=2)

```

```{r, echo=FALSE}

myPlotDensity<-function(index) 
  {plot(density(hbat[,index]), main=names(hbat[index]),ylab=names(hbat)[index])}

lapply(7:23, FUN=myPlotDensity)

```

